A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-26 text/survival.Rmd
incorporate Megan Hitchens' comments, fix spaces after parens

Our estimates of tissue-specific cluster effects, in contrast, ranged from less
than 1 up to about 3 or 4, reflecting that some clusters are either less deadly
or more deadly than other clusters within each cancer type (**Figure 9**). A
cluster-specific rate of 1 represents typical rate for this tissue type. For
several cancers ( _e.g._ PRAD, kidney chromophobe (KICH), diffuse large B-cell
lymphoma (DBLC), thyroid cancer (THCA)) the posterior estimates are largely
indistinguishable from the prior, reflecting that either there were too few
mortalities in the data to make an estimate (as expected for PRAD and THCA) or
two few samples, period. We did not observe cluster-specific trends that held
true across cancer types, which could result from different cancers having
different standards of care for example. In support of this interpretation, we
also tested a factored model which considered both cancer type and each cluster
independent of cancer type (not shown). Though we were able to successfully fit
this model, it is a special case of the more general model where cluster and
tissue independently affect longevity, and there is no reason to believe that
cluster specific effects would necessarily remain constant across tissue types
given how widely the patients vary across tissue types, drug and surgical
treatments.

>>>>

Our estimates of tissue-specific cluster effects, in contrast, ranged from less
than 1 up to about 3 or 4, reflecting that some clusters are either less deadly
or more deadly than other clusters within each cancer type (**Figure 9**). A
cluster-specific rate of 1 represents the typical rate for this tissue type. For
several cancers (\it{e.g.} PRAD, kidney chromophobe (KICH), diffuse large B-cell
lymphoma (DBLC), thyroid cancer (THCA)) the posterior estimates are largely
indistinguishable from the prior, reflecting that either there were too few
mortalities in the data to make an estimate (as expected for PRAD and THCA) or
two few samples, period. We did not observe cluster-specific trends that held
true across cancer types, which could result from different cancers having
different standards of care for example. In support of this interpretation, we
also tested a factored model which considered both cancer type and each cluster
independent of cancer type (not shown). Though we were able to successfully fit
this model, it is a special case of the more general model where cluster and
tissue independently affect longevity, and there is no reason to believe that
cluster specific effects would necessarily remain constant across tissue types
given how widely the patients vary across tissue types, drug and surgical
treatments.
